A Survey on Ordered Binary Decision Diagrams

### 2015-09-15 paper.tex
Finish BEDs

Analogous to OBDDs and FDDs, OBEDs and FBEDs can be defined, whereas OBEDs are
OBDDs without operator nodes. The reduction rule of BEDs is similar to the one
of OBDDs but extended with an additional rule for operator nodes. For any operator
nodes $n$ it has to hold that $lo(n)$ and $hi(n)$ are nonterminals in order to
guarantee reducedness. However, even if a BED is reduced, canonicity is not
guaranteed (in contrast to OBDDs).

\tbr

% balance columns on last page
\balance

>>>>

Analogous to OBDDs and FDDs, OBEDs and FBEDs can be defined, whereas OBEDs are
OBDDs without operator nodes. The reduction rule of BEDs is similar to the one
of OBDDs but extended with an additional rule for operator nodes. For any operator
nodes $n$ it has to hold that $lo(n)$ and $hi(n)$ are nonterminals in order to
guarantee reducedness. Apart from that, before generating a new node, an existence
check is performed. If there exists an equivalent node, this node is reused.
Otherwise the new node is created and considered in the next check. However, even
if a BED is reduced, canonicity is not guaranteed (in contrast to
OBDDs)~\cite{ANDERSEN97}.

Andersen and Hulgaard~\cite{ANDERSEN97} also introduced some checks especially
for operator nodes in order to reduce the BED-size even further. Moreover a
detailed description of how to convert a BED into an equivalent OBDD is provided,
distinguishing between step-by-step variable moving (denoted as \textit{up\_one})
and block-wise variable moving (denoted as \textit{up\_all}).

The \textit{up\_one} operation can be implemented with expected runtime of $O(n)$,
where $n$ denotes the number reachable of nodes from a given node. Nonetheless,
because BEDs are exponentially more succinct than OBDDs, the complete
transformation has an exponential worst-case complexity. Also \textit{up\_all} has
an exponential worst-case complexity (for the same reason)~\cite{ANDERSEN97}.

Andersen and Hulgaard~\cite{ANDERSEN97} concluded that \textit{up\_all} is a
memory efficient approach to construct OBDDs in contrast to the OBDD construction
from scratch, without actually increasing the runtime. \textit{up\_one} is used
to implement existential quantification and substitution efficiently, having
linear runtime complexity in the size of the BED. Reconsidering symbolic model
checking, BEDs can be used to evaluate fixed point computations directly without
converting it to an OBDD. Moreover, BEDs can perform fixed point computations more
efficiently because of their succinct representation~\cite{ANDERSEN97}. \tbr

\clearpage
% balance columns on last page
%\balance
